An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-26 scagnostics.Rmd
start on data section

Three data simulations are used for examining the behaviour of the index functions. Each generates special structure in two variables, and the remaining variables are noise. This construction means that variable selection would be sufficient for the identification of the structure. We use this setup for simplicity, and since all variable combinations are treated equally in the PP it does not affect our conclusions about the ability of identifying the structure in arbitrary linear combinations of variables.

>>>>

### Data construction
\label{sec:dataOv}

Three families of data simulations are used for examining the behaviour of the index functions. Each generates  structure in two variables, with the remaining variables containing various types of noise. This is a very simple construction, because there is no need for projection pursuit to find the structure, one could simply use the scagnostics on pairs of variables. However, it serves the purpose to also evaluate the PPIs. The three data families are:

- **pipe**: $p$ points where $n-1$ points are independently drawn from a uniform distribution between $[-1,1]$, and enforcing $x_n^2 + x_{n-1}^2 = 1 \pm 0.1$ by rejection sampling as an example of a dataset with special view that is not described by functional dependence, and where sampling boundaries are apparent in the distribution, labelled "pipe"
- **sine**:  $p$ points where $n-1$ points are independently drawn from a normal distribution with mean 0 and variance 1, and with $x_n = \sin(x_{n-1}) + \mathrm{jittering}$ as an example dataset with special view described by a function, labelled "sine"
- **sphere**:  $p$ points on an n-dimensional sphere randomly selected using the geozoo package [@geozoo], as an example of dataset without special views, labelled "sphere"

Two samples sizes are also used: $p=100$ (small) and $p=1000$ (large).

### Property assessment
